---
title: "AGEC 652 - Lecture 1.1"
subtitle: "A course introduction"
date: "Spring 2023"
author: "Diego S. Cardoso"
#institute: "Purdue University, Department of Agricultural Economics"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    # self_contained: true
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---
exclude: true
```{r setup}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  JuliaCall, xaringanthemer
)

options(htmltools.dir.version = FALSE)

knitr::opts_hooks$set(fig.callout = function(options) {
  if (options$fig.callout) {
    options$echo <- FALSE
  }

  knitr::opts_chunk$set(echo = TRUE, fig.align="center")
  options
})

```


```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#8E6F3E", 
  header_font_google = google_font("Josefin Sans"),
  text_font_size = "28px",
  colors = c(
    red = "#f34213",
    gold = "#CFB991",
    gray = "CFB991",
    blue = "#295fbe",
    black = "#000000"
  )
)

extra_css <- list(
  ".small" = list("font-size" = "90%"),
  ".big" = list("font-size" = "125%"),
  ".footnote" = list("font-size" = "60%"), 
  ".full-width" = list(
    display = "flex",
    width   = "100%",
    flex    = "1 1 auto"
  )
)

style_extra_css(css = extra_css)

```


```{julia}
using Pkg
Pkg.activate(".")
Pkg.instantiate()
Pkg.add("ForwardDiff"); Pkg.add("Distributions"); Pkg.add("Plots"); Pkg.add("BenchmarkTools")
```

---

# Welcome to AGEC 652!

- Formally: *Application of Quantitative Analysis: Mathematical Programming*

--

- Informally: **Computational methods for applied economics**


---

## What you will learn in this course

1. How to setup and manage computational projects for your research

--

2. Understand why and when computational methods can help

--

3. And, most importantly, how to apply many techniques to solve economic problems using your computer

---

## What we will cover

**3 parts**

1. An introduction to Scientific Computing for Applied Economics

2. Numerical methods to solve economic problems

3. Structural estimation of static models

--

  - .blue[.small[We leave out dynamic models. Those you'll see in AGEC 654]]

---

## What we will cover: Part I

*First 3 weeks*

- Reproducibility

- Version control (git) and project organization

- Julia programming language

---

## What we will cover: Part II

*Week 3 until 13*

- Fundamentals of numerical methods
  - Computer architecture and arithmetic
  - Numerical differentiation and integration
- Systems of equations
  - Methods for linear and nonlinear systems
  - Economic models and applications
- Function approximation  
  - Interpolation
  - Functional equations
- Optimization
  - Methods for constrained and unconstrained
  - Economic models and applications

---

## What we will cover: Part III

*Weeks 13 to 15*

- Introduction to structural estimation
  - Structural vs. reduced-form
  - Recap of MLE and GMM
  - Estimation of models with a single agent
  - Estimation of models with multiple (interacting) agents

--

.blue[.small[*Dates are tentative: This is a "new" course. Your feedback and understanding are appreciated.*]]

---

class: inverse, center, middle
name:introductions

# Let's stop here for a while and introduce ourselves!

---

## Course materials

- Papers, articles, and tutorials 
  - Links on *Brightspace > Content > Materials*
- Lecture slides, coding examples 
  - Links on *Brightspace > Content > Materials*
  - Hosted on the GitHub class repository (more details to come)
- Books
  1. Miranda and Fackler (2002)
  2. Judd (1998)
  3. Nocedal and Wright (2006)
  - .blue[.small[All available at Purdue Library, links on Brightspace]]
  

---


## What you need to succeed in this course

- AGEC 552 or ECON 615: matrix algebra and differential calculus. And some basic game theory.

--

- Previous coding experience or willingness to spend some time learning as you go

- A laptop to use in class (come talk to me if you do not have one available)

---

## What you have to do

- Come to class (unless unable)

- **Try** solving in-class quick problems and labs and submit your work right after class

- Solve Weekly Problems

- Do a mini-project

---

## Grading

- Here it gets a little more sophisticated than usual

--

- This course follows a modern approach called Standards-Based Grading
  - It's a more appropriate way to assess skills like the ones you will learn in this course

- You will need to demonstrate mastery over a pre-specified list of skills, or **learning standards**
  - There is no averaging of scores across assignments

--

- This is different from the traditional way. Let's take a look together at the syllabus to understand it

---

## Course and University policies

**Attendance**

- We follow standard Purdue regulations on attendance. But things are still weird with COVID... 

- If you must miss class for health or any other reason, please let me know as far in advance as possible by Purdue email

- And please **take care of yourself, physically and mentally**
  
---

## Course and University policies

**Course evaluation**

- There is the regular course evaluation by Purdue at the end of the semester

- In addition, I will ask for your anonymous and voluntary opinion halfway through the course
  - This is a new course with inevitable rough edges
  - Your sincere feedback is appreciated and will help me deliver a better course for everyone
  
.red[Please read the syllabus for other policies]

---


## Office hours

(From next week)

- Mondays 11 AM to 12 PM

- Wednesdays 1:30 PM to 2:30 PM (you have priority these days)

- I will schedule a meeting room for office hours. Typically, I'll be there and you can pop in at anytime with your laptop for help with the course (or general programming questions)


---

Before we continue, some

##.center[.blue[Acknowledgments]]

.center[*These slides build on materials provided by Ivan Rudik (Cornell University) and on the textbooks and other sources referenced in the syllabus/reading list.*]

---

class: inverse, center, middle
name: why

# Why computational methods?


---

## Why do we need computational methods?

Everything you've done so far has likely been solvable analytically

Including OLS: $\hat{\beta} = (X'X)^{-1}X'Y$

--

.red[Not all economic models have closed-form solutions, and others can't have closed-form solutions with losing important economic content]


---

## What can we compute?

We can use computation + theory to answer **quantitative** questions

--

Theory can't give us welfare in dollar terms

Theory can't tell us the value of economic primitives


---

## What can we compute?

Theory often relies on strong assumptions like:

--

- log utility (income loss vs substitution)
- no transaction costs (important friction)
- strictly concave objectives (natural phenomena don't follow this)
- static decision-making

It can be unclear what the cost of these assumptions are

---

class: inverse, center, middle
# Some apparently simple questions

---

## Example 1

Suppose we have a constant elasticity demand function: 

$$q(p) = p^{-0.2}$$

In equilibrium, quantity demanded is $q^* = 2$

**Q: What price clears the market in equilibrium?**

---

## Example 1

A: Just invert the demand function

$$2 = p^{-0.2}$$

--

$$p^* = 2^{-5} \checkmark$$

Your calculator can do the rest

---

## Example 2

Suppose the demand function is now

$$q(p) = 0.5p^{-0.2} + 0.5p^{-0.5},$$

a weighted average of two CE demand functions

In equilibrium, quantity demanded is $q^* = 2$

**Q: What price clears the market in equilibrium?**

--

First, does a solution exist?

--

Yes, why?

---

## Example 2

$q(p)$ is continuous and monotonically decreasing

--

$q(p)$ is greater than 2 at $p=0.1$ and less than 2 at $p=0.2$

--

$\Rightarrow$ by intermediate value theorem $q(p) = 2$ somewhere in $(0.1,0.2)$

---

## Example 2

```{julia, results = 'hide'}
# We know solution is between .1 and .2
x = collect(range(.1, stop = .2, length = 10)) # generate evenly spaced grid
q_d = ones(size(x)).*2 # generate equal length vector of qd=2

# Define price function
price(p) = p.^(-0.2)/2 .+ p.^(-0.5)/2

# Get corresponding quantity values at these prices
y = price(x)

```

Now plot $q_d$ and $q(p)$

---

## Example 2

```{julia, echo = FALSE}
using Plots
plot(x, [y q_d],
    linestyle = [:solid :dot],
    linewidth = [3 3],
    linecolor = [:red :blue],
    tickfontsize = 12,
    grid = :no,
    xlabel = "p",
    ylabel = "q(p)",
    label = ["q(p)" "Quantity Demanded"])
```


---

## Example 2

Notice: if we let $t = p^{-0.1}$ then

$$q(t) = 0.5t^2 + 0.5t^5$$

--

Can we solve for $t$ now?

--

No! Closed-form solutions to fifth order polynomials are not guaranteed to exist!

--

So how do we solve the problem?

---

## Newton's method

Iteratively do the following:
1. Guess solution to: $q(p) - q^* = 0 \Rightarrow q(p) - 2 = 0$
2. Approximate the function with local 2nd-order polynomial around guess
3. Solve this easier equation
4. Solution is the new guess
5. Stop if previous guess and new guess are sufficiently close

We will learn more about this and why it works in a later class

---

## Coding Newton's method

```{julia, results = 'hide'}
# Define demand functions
demand(p) = p^(-0.2)/2 + p^(-0.5)/2 - 2     # demanded quantity minus target
demand_grad(p) = .1*p^(-1.2) + .25*p^(-1.5) # demand gradient
```

--

```{julia, results = 'hide'}
function find_root_newton(demand, demand_grad)
    p = .3        # initial guess
    deltap = 1e10 # initialize stepsize

    while abs(deltap) > 1e-4
        deltap = demand(p)/demand_grad(p)
        p += deltap
        println("Intermediate guess of p = $(round(p,digits=3)).")
    end
    println("The solution is p = $(round(p,digits=3)).")
    return p
end;
```

---

## Newton code

```{julia}
# Solve for price
find_root_newton(demand, demand_grad)
```

---

## Example 3

Consider a two period ag commodity market model

- Period 1: Farmer makes acreage decisions for planting  
- Period 2: Per-acre yield realizes, equilibrium crop price clears the market

--

The farmer's policy function is: 

$$a(E[p]) = \frac{1}{2} + \frac{1}{2}E[p]$$

---

## Example 3

Yield $\hat{y}$ is stochastic and only realized after planting period. It follows $\hat{y} \sim \mathcal{N}(1, 0.1)$


Crop production is 

$$q = a\hat{y}$$

--

Demand is given by 

$$p(q) = 3-2q$$

--

**Q: How many acres get planted?**

---

## Example 3

**Q: How many acres get planted?**

A: We plug in the stochastic quantity and take expectations

$p(\hat{y}) = 3-2a\hat{y}$

--

$a = \frac{1}{2} + \frac{1}{2}(3-2aE[\hat{y}])$

--

Rearrange and solve:

$a^* = 1$

---

## Example 3

Now suppose the government implements a price floor such that $p > 1$. 

We now have that 

$$p(\hat{y}) = \max(1,3-2a\hat{y})$$

**Q: How many acres get planted with a price floor?**

---

## Example 3

**Q: How many acres get planted with a price floor?**

This is analytically intractable

--

The max operator is non-linear so we can't pass the expectation through

$E[\max(1,3-2a\hat{y})] \neq \max(1,E[3-2a\hat{y}])$

--

**We need to solve this numerically**

---

## Function iteration

.small[We can solve this using a technique called **function iteration**]

```{julia, results = 'hide'}
# Function iteration method to find a root
function find_root_fi(mn, variance)

    y = randn(1000)*sqrt(variance) .+ mn # draws of the random variable
    a = 1.                               # initial guess
    differ = 100.                        # initialize error
    exp_price = 1.                       # initialize expected price

    while differ > 1e-4
        a_old = a                      # save old acreage
        p = max.(1, 3 .- 2 .*a.*y)     # compute price at all distribution points
        exp_price = mean(p)            # compute expected price
        a = 1/2 + 1/2*exp_price        # get new acreage planted given new price
        differ= abs(a - a_old)         # change in acreage planted
        println("Intermediate acreage guess: $(round(a,digits=3))")
    end

    return a, exp_price
end
```

---

## Function iteration

```{julia}
acreage, expected_price = find_root_fi(1, 0.1)
println("The optimal number of acres to plant is $(round(acreage, digits = 3)).\nThe expected price is $(round(expected_price, digits = 3)).")
```

---

# Don't leave just yet!

**Things to do before next class**

1. Read Gentzkow and Shapiro (2014) *Code and Data for the Social Sciences*
2. Watch the 5-minute video *What is version control?*
  - .small[.blue[Links for both are on Brightspace > Content > Materials]]

3. Create a GitHub account with your Purdue email (or add it to your existing account)
4. Install [GitHub Desktop](https://desktop.github.com/)

