---
title: "AGEC 652 - Lab for unit 2.2"
subtitle: "Calculating moments of nonlinear functions"
date: "Spring 2023"
author: "Diego S. Cardoso"
#institute: "Purdue University, Department of Agricultural Economics"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---
exclude: true
```{r setup}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  xaringanthemer, JuliaCall
)

#options(htmltools.dir.version = FALSE)

knitr::opts_hooks$set(fig.callout = function(options) {
  if (options$fig.callout) {
    options$echo <- FALSE
  }

  knitr::opts_chunk$set(echo = TRUE, fig.align="center")
  options
})

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#8E6F3E", 
  header_font_google = google_font("Josefin Sans"),
  text_font_size = "28px",
  colors = c(
    red = "#f34213",
    gold = "#CFB991",
    gray = "#C0C0C0",
    blue = "#295fbe",
    black = "#000000"
  )
)

extra_css <- list(
  ".small" = list("font-size" = "90%"),
  ".big" = list("font-size" = "125%"),
  ".footnote" = list("font-size" = "60%"), 
  ".full-width" = list(
    display = "flex",
    width   = "100%",
    flex    = "1 1 auto"
  )
)

style_extra_css(css = extra_css)

```

```{julia}
using Pkg
Pkg.activate(".")
Pkg.instantiate()
Pkg.add("Plots"); Pkg.add("Distributions");
```

---

## Problem 

We are interested in estimating the mean and variance of household consumption of a good whose demand function is given by

$$q(y) = \phi \tilde{y}^\alpha$$

where $\phi, \alpha > 0$.

Income levels $\tilde{y}$ are log-normally distributed. This means that the log of $y$ are normally distributed, with mean $\mu$ and standard deviation $\sigma$.

---

## Problem

$$q(y) = \phi \tilde{y}^\alpha$$

Calculate

a. $E[q(y)]$

b. $Var[q(y)]$

with $\phi = 11$, $\alpha = 0.1$, $\mu = 60$, and $\sigma = 1.5$. 

Use `QuantEcon.qnwlogn` function to calculate $n=15$ nodes and weights of a quadrature method specific for log-normal distributions.

---

## Setup

Import the necessary packages

```{julia}
using QuantEcon, Distributions;
using Plots; # We'll use this to plot the distribution
```


---

## Setup

Define the model parameters

```{julia}
ϕ = 11;
α = 0.1;
μ = 60;
σ = 1.5;
```


---

## Plotting the distribution

Let's take a look at the income distribution for this problem

```{julia}
y_dist = LogNormal(log(μ), log(σ)); # Define the distribution over which we integrate
```

```{julia, out.height="40%"}
plot(0:200, pdf.(y_dist, 0:200), label="PDF of y") # Plot its PDF
```


---

.blue[Your turn, part A]

Calculate $E[q(y)]$. To do so

1. Define function `q(y)`.
  1. Try out a few values around the mean income to get a sense of the magnitude
2. Use the `QuantEcon.qnwlogn` function with 15 nodes to calculate the nodes and weights
  1. Note that you need to take the logs of $\mu$ and $\sigma$!
3. Calculate the expectation using the quadrature method
  1. Check: is $E[q(y)] = q(E[y])$? 

---

.blue[Your turn, part B]

Calculate $Var[q(y)]$. To do so, Remember: $Var[X] = E[X^2] - E[X]^2$

1. Calculate the expectation of the square
  1. The distribution is the same, so you can use the same nodes and weights!
2. Use your answer from part A to calculate the second term
3. Compute the variance using the terms from items 1 and 2


